---
title: "ModelEM_Performance"
author: "Cassidy Peterson"
date: "July 2023"
output: html_document
---

```{r setup, include=FALSE}
# library(knitr)
knitr::opts_chunk$set(echo = TRUE, autodep = TRUE, cache=TRUE)
# library(openMSE)
# library(vioplot)
setwd('C:\\Users\\cassidy.peterson\\Documents\\Github\\SAtl_Climate_MSE')
# knitr::opts_knit$set(root.dir = 'C:\\Users\\cassidy.peterson\\Documents\\Github\\SAtl_Climate_MSE')
source("get_testEM_results.R")
source("get_terminalEM_results.R")

```

## Background

This document shows the performance of the model-based EMs from a South Atlantic MSE exercise for black sea bass (BSB), vermilion snapper (VS), and red porgy (RP) using the openMSE software ([Blue Matter Science](bluematterscience.com)). 




# First SCA application 
These first round of analyses are based on the base-case OM scenario at the end of the historical period compared to the first application of the EM. 

## VS Model-EM Results

```{r VS-OMRec, echo=FALSE, fig.height=6, cache=TRUE,  fig.cap = "VS OM Recruitment Dynamics"}

# testOM<-testOM_BlackSeaBass
# testEM<-testEM_BlackSeaBass
# sp<-"BSB"
testOM<-testOM_VermilionSnapper
testEM<-testEM_VermilionSnapper
sp<-"VS"
# testOM<-testOM_RedPorgy
# testEM<-testEM_RedPorgy
# sp<-"RP"
# 
evalEM_<-evalEM(testOM, testEM)

hst<-OM_Perry_hist(testOM, title=paste0(sp," OM recruitment dynamics"))
```

EM estimates are presented relative to OM-designated values (e.g., (EMval - OMval)/OMval). 
```{r VS-EM, echo=FALSE, fig.height=8, fig.cap = "VS EM relative performance"}

# length(evalEM_)
par(mfrow=c(3,3))
for(i in 1:length(evalEM_)){
  if(names(evalEM_)[i]!="NLL") {
      hist(evalEM_[[i]], main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
  if(names(evalEM_)[i]=="NLL") {
    hist(evalEM_[[i]]$Total, main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
}
```


## BSB Model-EM Results


```{r BSB-OMRec, echo=FALSE, fig.height=6, cache=TRUE,  fig.cap = "BSB OM Recruitment Dynamics"}

testOM<-testOM_BlackSeaBass
testEM<-testEM_BlackSeaBass
sp<-"BSB"
# testOM<-testOM_VermilionSnapper
# testEM<-testEM_VermilionSnapper
# sp<-"VS"
# testOM<-testOM_RedPorgy
# testEM<-testEM_RedPorgy
# sp<-"RP"
# 
evalEM_<-evalEM(testOM, testEM)

hst<-OM_Perry_hist(testOM, title=paste0(sp," OM recruitment dynamics"))
```

EM estimates are presented relative to OM-designated values (e.g., (EMval - OMval)/OMval). 
```{r BSB-EM, echo=FALSE, fig.height=8, fig.cap = "BSB EM relative performance"}

# length(evalEM_)
par(mfrow=c(3,3))
for(i in 1:length(evalEM_)){
  if(names(evalEM_)[i]!="NLL") {
      hist(evalEM_[[i]], main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
  if(names(evalEM_)[i]=="NLL") {
    hist(evalEM_[[i]]$Total, main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
}
```


## RP Model-EM Results


```{r RP-OMRec, echo=FALSE, fig.height=6, cache=TRUE,  fig.cap = "RP OM Recruitment Dynamics"}

# testOM<-testOM_BlackSeaBass
# testEM<-testEM_BlackSeaBass
# sp<-"BSB"
# testOM<-testOM_VermilionSnapper
# testEM<-testEM_VermilionSnapper
# sp<-"VS"
testOM<-testOM_RedPorgy
testEM<-testEM_RedPorgy
sp<-"RP"
# 
evalEM_<-evalEM(testOM, testEM)

hst<-OM_Perry_hist(testOM, title=paste0(sp," OM recruitment dynamics"))
```

EM estimates are presented relative to OM-designated values (e.g., (EMval - OMval)/OMval). 
```{r RP-EM, echo=FALSE, fig.height=8,  fig.cap = "RP EM relative performance"}

# length(evalEM_)
par(mfrow=c(3,3))
for(i in 1:length(evalEM_)){
  if(names(evalEM_)[i]!="NLL") {
      hist(evalEM_[[i]], main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
  if(names(evalEM_)[i]=="NLL") {
    hist(evalEM_[[i]]$Total, main=paste0(sp," ", names(evalEM_)[i]), xlab="")
  }
}
```





# Final SCA application
These second round of results are comparing SCA-based EM results to the OM dynamics at the final SCA application of the simulation. Plots show histograms of relative error ( EMest-OMval)/OMval ) of EM-estimated values. The bars are colored in gray-scale based on MP, and the bar borders are colored based on the OM scenario. 


```{r VS-final-EM, echo=FALSE, fig.height=9,  fig.cap = "VS final EM relative performance"}
sp<-"VS"
tEMres<- get(paste0(sp,"_tEM"))

# run plotting loop for every em perf metric (p)
for(p in names(tEMres[[s]][[mp]]) ){
  Plot_tEMres(tEMres, p)
} # end p loop

```

```{r BSB-final-EM, echo=FALSE, fig.height=9,  fig.cap = "BSB final EM relative performance"}
sp<-"BSB"
tEMres<- get(paste0(sp,"_tEM"))

# run plotting loop for every em perf metric (p)
for(p in names(tEMres[[s]][[mp]]) ){
  Plot_tEMres(tEMres, p)
} # end p loop

```

```{r RP-final-EM, echo=FALSE, fig.height=9,  fig.cap = "RP final EM relative performance"}
sp<-"RP"
tEMres<- get(paste0(sp,"_tEM"))

# run plotting loop for every em perf metric (p)
for(p in names(tEMres[[s]][[mp]]) ){
  Plot_tEMres(tEMres, p)
} # end p loop

```
