---
title: "Climate-readiness of empirical vs. model-based MPs in the US South Atlantic - Red Porgy"
author: "Cassidy Peterson"
date: "August 2024"
output: 
  html_document:
    toc: true
    toc_float: true
  github_document:
        html_preview: FALSE
---

```{r setup, include=FALSE}
# library(knitr)
knitr::opts_chunk$set(echo = TRUE, autodep = TRUE)#, cache=TRUE)
# knitr::opts_knit$set(root.dir="..")
setwd('C:\\Users\\cassidy.peterson\\Documents\\Github\\SAtl_Climate_MSE')
# library(openMSE)
# library(vioplot)
source("Analyze_Results_Setup.R")

```

# Background

Supplement to Peterson CD. Klibansky N. Vincent MT. Walter III JF. Climate-readiness of fishery management procedures with application to the southeast U.S. Atlantic. 

This report contains supplementary materials from a South Atlantic MSE exercise testing the behavior of model-based versus empirical MPs for black sea bass (BSB), vermilion snapper (VS), and red porgy (RP) using the openMSE software ([Blue Matter Science](bluematterscience.com)).

This section is focused on results for red porgy. 

## Abbreviations 

* MSE abbreviations
  + MSE - management strategy evaluation
  + OM - operating model
  + MP - management procedure
  + PM - performance metrics

* Case study species
  + VS - vermilion snapper
  + BSB - black sea bass
  + RP- red porgy

* Management procedures (MP). Refer to [openMSE](openmse.com) and [dlmtool](https://dlmtool.openmse.com/reference/index.html) documentation for further details on each MP. Note that all non-SCA MPs are empirical (indicator-based) MPs
  + ZeroC - zero catch MP, used for demonstration purposes only. 
  + SCA*x* - statistical catch at age model that occurs every *x* years; may also be specified by a c or p (e.g., SCA5_c) to indicate that catches between assessments are constant (c) or specified by assessment forecast / projections
  + GBtarg - Gt - Geromont and Butterworth target CPUE and catch MP 
  + ICI - index confidence interval MP
  + Irat - Ir - Iratio - mean index ratio
  + IT10 - I10 - iterative index target MP
  + Itarg - It - Itarget - incremental index target MP
  + GBslope - Gs - Geromont and Butterworth index slope MP
  + Islope - Is - index slope tracking MP

* Operating model (OM) scenarios 
  + Base - base-case OM with no nonstationarity
  + recdev_hi - Mean recruitment deviations in normal space was linearly adjusted to a value twice the size of the historical value from years 11-20 and remained at the shifted value until projection year 50
  + recdev_lo - Mean recruitment deviations in normal space was linearly adjusted to a value half the size of the historical value from years 11-20 and remained at the shifted value until projection year 50
  + age0M_hi - A shift in age-0 natural mortality simulated by linearly increasing age-0 M from the historical value to twice the historical value from years 11-20 and remaining at the higher value until projection year 50
  + age0M_lo - A shift in age-0 natural mortality simulated by linearly decreasing age-0 M from the historical value to half the historical value from years 11-20 and remaining at the lower value until projection year 50
  + recns - Base case recruitment deviations are multiplied by a random walk vector with a mean of 1 and standard deviation of 5 (using random_walk function in [bamExtras](https://github.com/nikolaifish/bamExtras) version 0.0.1 R package)
  + epiM - A multiplier greater than 1 is applied to historical natural mortality (M) in 10% of years; multiplier was defined as $1+lognormal(\mu = 0$,$\sigma = 0.2$) with a maximum value of 3 for red porgy or 4 for black sea bass and vermilion snapper
  + uobs_hi - The coefficient of variation (CV) of the survey index was linearly increased from the value from the last year of the historical period to twice that level over years 11-20 and remaining at the higher value until projection year 50
  + uobs_lo - The CV of the survey index was linearly decreased from the value from the last year of the historical period to half that level over years 11-20 and remaining at the higher value until projection year 50

* Performance metrics (PMs)
  + $dSSB_{0}$ - dynamic spawning stock biomass that would occur under no fishing pressure
  + $F_{MSY}$ - the rate of fishing mortality ($F$) that would produce MSY 
  + $SSB_{MSY}$ - SSB that would produce MSY if fished at $F_{MSY}$ 
  + $SSB_{y}$ - SSB in the year $y$
  + SSBratio	- The ratio of SSB to dynamic SSB that would be achieved in the absence of fishing ($dSSB_{0}$) calculated annually
  + t10SSBratio - Mean terminal 10 years of SSBratio; SSBratio calculated annually over the final 10 years of the projection period and averaged across years 40-50
  + Fratio - The ratio of realized fishing mortality ($F$) to the rate that would produce MSY ($F_{MSY}$) calculated annually
  + PNOF - Probability of not overfishing, calculated as the proportion of years that $F/F_{MSY}$ exceeds 1 for the 50-year projection period of each projection iteration
  + P100 - Proportion of years in the final 10 years of the simulation period (years 40-50) in which SSB>SSBMSY for each projection iteration
  + cyield - Cumulative relative yield, where relative yield is calculated as realized yield relative to OM-defined MSY (i.e., if yield = MSY, then relative yield = 1 for that year) summed across all 50 projected years
  + AAVY - Annual average variability in yield, calculated as the average change in yield from year-to-year across all years of the projection period: $AAVY= \Sigma_{t=0}^{t=50} sqrt( (((yield_{t}-yield_{t-1}) / (yield_{t-1} ))^{2}) )$




# Red Porgy Results

```{r RP-FOUNDATION, setup, include=FALSE, cache=TRUE, cache.lazy=FALSE}
# knitr::opts_chunk$set(cache = TRUE) # do not re-run if unnecessary

##### INPUTS ######
set.file<-"MSE_obj/"
species<-"RedPorgy"; sp<-"RP"


orderedMPs<-c(1:13)  #c(11,1, 12:13, 2:10) #c(1, 10:11, 2:9, 12:13) #c(1, 9:10, 2:8)
orderedScenarios<-c(3, 5,6,4,1,2,7,10,11) #c(3,5:6,4,1:2,7:11)
scenarios<-c("base","recdev_hi", "recdev_lo", "epiM", "age0M_hi", "age0M_lo",
             "recns", "uobs_hi", "uobs_lo") 

    MP_namesR_leg<-c("ZeroC","SCA1","SCA5_c","SCA10_c","SCA5_p","SCA10_p",
                     "GBtarg","ICI","Irat","IT10","Itarg",
                     "GBslope","Islope")
    MP_namesR_abbrev<-c("ZC","S1","5c","10c","5p","10p", "Gt",
                        "ICI","Ir","I10","It","Gs","Is")

  MP_R_col=c('grey15','grey30','gray40','gray50','gray60','gray70','deepskyblue4','deepskyblue3','deepskyblue','skyblue3','cadetblue1','cadetblue', 'lightseagreen') 

# par.args<-list(mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
par.args<-list(mar=c(0.5, 0.5, 0.2, 0.2), mgp=c(0.7, 0.25, 0), tck=-0.01, cex.axis=1)
par(par.args)


### Run FUNCTIONS for input species #####
assign(sp, GetResults(species1=species,sp1=sp)) # save GetResults with sp | SP

# correct results for EpiM SSB nonsensical results
sptemp<-get(sp)                       # save SP as sptemp
summary(sptemp$epiM@SB_SBMSY)         # see nonsensical sptemp results
assign(sp, EpiMDeal(sptemp))          # deal with nonsensical results -- resave as SP
summary(get(sp)$epiM@SB_SBMSY)        # see updated results
remove(sptemp)

# Get performance metrics and reorder
CollatePMs_temp<-CollatePMs(sp)
assign(paste(sp,"PMs",sep='_'), CollatePMs_temp$returnlist) #SP_PMs -- UNORDERED
assign(paste(sp, "PM", sep="_"), Reorder_MPs(get(paste0(sp,"_PMs"))) ) #SP_PM ## REORDERED PERF METRICS
assign(paste(sp, "PMs_nest", sep="_"), CollatePMs_temp$returnlist_nest ) #SP_PMs_nested -- UNORDERED ##
assign(paste(sp, "PM_nest", sep="_"), Reorder_MPs(get(paste0(sp,"_PMs_nest")), nested=TRUE) ) #SP_PM ## REORDERED PERF METRICS REORDERED PERF METRICS

# Get performance metrics relative to base OM case
assign(paste(sp,"RelPM_rd", sep='_'), Relative_MP_Perf_rd(sp)) #SP_RelPM_rd

```


## Median Trajectory Plots

Below plots demonstrate median trajectories across 250 iterations per OM and MP scenario. Note y-axis limits. 


### Median SSBratio trajectory 

```{r echo=FALSE, fig.height=9,  fig.cap = "Median SSBratio ($SSB / dSSB_{0}$) trajectories for each MP in each OM."}
# exercise.setup="PreviousChunk",
par(mfrow=c(4,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
reflinetemp<-get(sp)[[1]]@OM$SSBMSY_SSB0[1]
Plot_SSBtraj_dSSB0(fsh=sp, refline=reflinetemp, subset=c(1:13))

```

### Median $SSB / SSB_{MSY}$ trajectory

Note that changes to recruitment deviations are not reflected in MSY-based reference points. 

```{r echo=FALSE, fig.height=9,  fig.cap = "Median $SSB / static SSB_{MSY}$ trajectories for each MP in each OM."}
par(mfrow=c(4,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
Plot_SSBtraj_MSY(fsh=sp, ylimsRDHi=c(0,7))

```

### Median catch trajectory

```{r echo=FALSE, fig.height=9,  fig.cap = "Median catch trajectories for each MP in each OM."}

par(mfrow=c(4,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
Plot_Catchtraj(fsh=sp, subset=c(2:13))

```

### Median SSBratio trajectory with 90% CIs

```{r echo=FALSE, fig.height=9,  fig.cap = "Median SSBratio ($SSB / dSSB_{0}$) trajectories for each MP with 90% confidence intervals. Each MP is plotted in a single coordinate for each OM scenario for simplicity."}
 
par(mfrow=c(4,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1, oma=c(0,0,1.2,0) )
Plot_SSBtraj_dSSB0_CI(fsh=sp, subset=c(2:13),refline=reflinetemp, legend=F)
```



## Violin plots

Below plots demonstrate distribution of performance metrics across 250 iterations per OM and MP scenario. Note y-axis limits. 


### Biomass 

```{r RP-biomass1-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Relative $SSB/SSB_{MSY}$ at year 30 by MP for each OM."}
par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
reflinetemp<-get(sp)[[1]]@OM$SSBMSY_SSB0[1]
myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='relSSB30', ylimsEpiM=c(0,5), legend=F, mf=c(3,3))

```


```{r RP-biomass2-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Relative SSBratio ($SSB / dSSB_{0}$) at year 30 (reldSSB030) by MP for each OM. Horizontal reference line is indicative of $SSB_{MSY}/SSB_{0}$ calculated at the OM conditioning step; note that this reference value may change over the projection period as population dynamics change, which is not considered for this illustration."}
par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
reflinetemp<-get(sp)[[1]]@OM$SSBMSY_SSB0[1]
myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='reldSSB030', refline2=reflinetemp, ylims=c(0,1.15), legend=F, mf=c(3,3))

```


### Fishing mortality 

```{r RP-F1-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Relative $F/F{MSY}$ at year 30 by MP for each OM."}
par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='relF30', ylimsEpiM=c(0,25), legend=F, mf=c(3,3))
```


```{r RP-F2-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Probability of not overfishing (PNOF) across the 50-year projection period by MP for each OM."}
par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='PNOF', legend=F, mf=c(3,3))
```


### Yield 


```{r RP-Yield1-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Relative yield (yield / MSY) at projection year 30 by MP for each OM."}
 par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
 myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='yield30', legend=F, mf=c(3,3),ylimsrecns=c(0,10))
```


```{r RP-Yield2-PM, echo=FALSE, fig.height=5, fig.width=9, fig.cap = "Cumulative relative yield (yield / MSY) at projection year 30 by MP for each OM."}
 par(mfrow=c(3,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
 myPlot_Violin(get(paste0(sp,"_PM_nest")), stat='cyield30', refline1=30, legend=F, mf=c(3,3),ylimsrecns=c(0,400))
```

## Cumulative Violin Plots (Across all OMs)

Below plots demonstrate distribution of performance metrics across all iterations, OMs, and MPs. Note y-axis limits. 


```{r RP-cumulative-PM-plot, echo=FALSE, fig.height=5, fig.width=7, fig.cap = "MP performance across OMs"}
par(mfrow=c(2,3), mar=c(2.4, 2.4, 0.2, 0.2), mgp=c(1.1, 0.25, 0), tck=-0.01, cex.axis=1)
reflinetemp<-get(sp)[[1]]@OM$SSBMSY_SSB0[1]
PlotCumPM(sp, Pstat="AAVY", refline=c(0.3), title=species, ylims=c(0,1)) # for BSB_O ylims=c(0,5) |for VS ylims=c(0,5)
PlotCumPM(sp, Pstat="PNOF", refline=c(0.5), title=species, ylims=c(0,1.1))
PlotCumPM(sp, Pstat="P100", refline=c(0.5), title=species, ylims=c(0,1.1))
PlotCumPM(sp, Pstat="relSSB30", refline=c(1), title=species, ylims=c(0,10))
PlotCumPM(sp, Pstat="relF30", refline=c(1), title=species, ylims=c(0,7))
PlotCumPM(sp, Pstat="cyield",  refline=c(50), title=species, ylims=c(0, 150))
```
